---
title: "Data Cleaning DS C1"
author: "Umair Waseem"
date: "2022-09-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Loading specific libraries:
```{r}
library("tidyverse")
library("dplyr")
library("lubridate")
```


## Loading our dataset


```{r dataloading}
dfRaw <- read_csv("Data/Data - DS C1 Course.csv")
head(dfRaw, n=10)

# To check how many number of columns and rows we have, simply using dim command
dim(dfRaw)
colnames(dfRaw)
```
```{r}
colnames(dfRaw)


```
## DataColumns renaming
```{r}
#column renaming
dataRenamed <- dfRaw |>
  rename("Id" = "Student ID",
         "Date_time" = "Timestamp",
         "uniName" = "Name of University or College currently or previously attended?")

names(dataRenamed[1:10])
#dataSelected <- column_to_rownames(dataSelected , var = "Id")
```
## Variable Selection

```{r Variable Selected for analysis}

dataSelected <- select(dataRenamed, Id, Date_time, uniName)


head(dataSelected, n = 5)

```

# Correcting date_Time feature  for getting dates out of it

```{r}
class(dataSelected$Date_time)
dataSelected$Date_time <- lubridate::mdy_hms(dataSelected$Date_time)
class(dataSelected$Date_time)
dataSelected <- tidyr::separate(dataSelected, Date_time, c("Date", "Time"), sep = " ")
dataSelected$Date <- lubridate::ymd(dataSelected$Date)





```

## Now We go with the column uniName and find out Uni names typed differently and merge them to single new variable

```{r}
dataSelected |> select(uniName) |>
  unique() |> count()



# So we have fount that out of 247 there are 143 unique values that means there is same universities mis-typed differently. So our next goal is to find those values and store to a new column under same flag name. 

unique(dataSelected$uniName)






```
```{r}
dataCategorized <- dataSelected |>
  mutate(University = case_when(
    str_detect(uniName, "IBA|Institute of Business Administration|Iba Karachi|IBA, Karachi|Iba Karachi|institute of business administration|Institute of business administration|INSTITUTE OF BUSINESS ADMINISTRATION KARACHI|Institute Of Business Administration|Institute Of Business Administration, Karachi|Institute of Business Adminstration|Institute of business administration karachi|INSTITUTE OF BUISNESS ADMINISTRATION KARACHI" 
  ) ~ "IBA",
  str_detect(
    uniName, "Azam|Quaid I azam university|Quaid-I-Azam University, Islamabad|Quaid e Azam University|Quaid e Azam university       Islamabad|Quaid-e-Azam University Islamabad|Quaid-i-Azam University Islamabad|Quaid e Azzam university Islamabad"
  ) ~ "QU",
  str_detect(
    uniName, "Sir syed university of Engineering Technology|Sir syed university of engineering and technology|Sir Syed University|Sir Syed University Of Engineering And Technology|Sir Syed University Of Engineering & Technology|Sir syed University of engineering and technology|Sirsyed university of engineering and technology|Sir Syed University of Engineering and Technology|Sir Syed university of engineering and technology|Sur Syed University of Engineering and Technology|Sir Syed University Engineering Technology" 
    ) ~ "SirSyed",
  str_detect(
    uniName,  "Ned university|NED University of Engineering and Technology Karachi|NED|Ned University"
      ) ~ "NED",
  str_detect(
    uniName, "IQRA|Iqra|iqra|iqra university") ~ "IQRA",
  str_detect(uniName, "Sindh|Smiu") ~ "SMIU" ,
  str_detect(uniName, "Karachi|University of karachi") ~ "KU",
  str_detect(uniName, "Szabist", ) ~ "SZABIST",
  str_detect(uniName, "Management|management", ) ~ "IOBM",
  str_detect(uniName, "University of engineering and technology Peshawar|University of Engineering and Technology Peshawar|University of Engineering and Technology Taxila") ~ "UET",
  str_detect(uniName, "COMSATS|Comsats|comsats")~ "COMSATS",
  str_detect(uniName, "LUMS|Lums|Lahore University of Management Sciences")~ "LUMS",
  str_detect(uniName, "Virtual|virtual|VIRTUAL")~ "VU",
  str_detect(uniName, "Bahria|bahria|BAHRIA")~ "Bahri",
  str_detect(uniName, "Bahria|MEHRAN|Mehran")~ "Mehran University of Engineering",
  
  TRUE ~ uniName  #keep all others same
  
  
  )
  
      )


unique(dataCategorized$University)  #this function will return unique value out of column/feature
colnames(dataCategorized)
```
Now we'll look into location columns and we are selecting two columns country and city, first we'll check unique values in it then cleaning in next step.

```{r}
dataLoc <- select(dfRaw, "Which Country are you currently residing in?", "Which City are you currently residing in?")

colnames(dataLoc)

unique(dataLoc$`Which Country are you currently residing in?`)
```
```{r}
dataLoc<- dataLoc |>
  mutate(Country = case_when(
    str_detect(`Which Country are you currently residing in?`, "Pakistan|PK|pakistan|Karachi|KARACHI|pk|Lahore|PAKISTAN")~"Pakistan",
    TRUE ~ `Which Country are you currently residing in?`
  )         )

unique(dataLoc$Country)

```
```{r}
# Now City Column
unique(dataLoc$`Which City are you currently residing in?`)

dataLoc<- dataLoc |>
  mutate(City = case_when(
    str_detect(`Which City are you currently residing in?`,
               "Karachi|KARACHI|karachi")~"Karachi",
    str_detect(`Which City are you currently residing in?`,
               "Islamabad|islamabad|ISLAMABAD")~"Islamabad",
    str_detect(`Which City are you currently residing in?`,
               "Abbottabad|abbottabad")~"Abbottabad",
    str_detect(`Which City are you currently residing in?`,
               "Pakistan")~"Not Specified",
      TRUE ~ `Which City are you currently residing in?`
  )         )

unique(dataLoc$City)
```
Now we move forward to Degree column and see whats the challenge here



```{r}

 dataCategorized <- dataCategorized |> mutate(Degree =case_when(
  str_detect(dfRaw$`Discipline of Degree?`,
             "Software|software|SE|SOFTWARE ENGINEERING")~"BS Software Engineering",
  str_detect(dfRaw$`Discipline of Degree?`,
             "Computer|Bcs|COMPUTER|CS|computer|BsCs|Bscs|Bs CE")~"Compute Science",
  str_detect(dfRaw$`Discipline of Degree?`,
             "Business Adminsitration|business administration|BBA-H|MBA|BBA (honor)|BBA")~"Business Administration",
  str_detect(dfRaw$`Discipline of Degree?`,
             "Economics|economics|economic")~"Economics",
  str_detect(dfRaw$`Discipline of Degree?`,
             "Data Science|data science|DATA SCIENCE|Data science")~"Data Sciences",
  str_detect(dfRaw$`Discipline of Degree?`,
             "Electrical Engineering|Electrical engineering|Electronics Engineering")~"Electrical Engineering",
  str_detect(dfRaw$`Discipline of Degree?`,
             "Yes|I'm very puntual")~"Incomplete Infromation",
   str_detect(dfRaw$`Discipline of Degree?`,
             "Finance|Accounting|accounting and Finance|accounting and finance")~"Accounting and Finance",
  str_detect(dfRaw$`Discipline of Degree?`,
             "Statistics|statistics")~"Statistics",
  str_detect(dfRaw$`Discipline of Degree?`,
             "Artificial Intelligence|Artificial intelligence|BS AI")~"BS in AI",
    TRUE ~ dfRaw$`Discipline of Degree?`
) )

```


```{r}
#unique(dataCategorized$Degree)
colnames(dataCategorized)
colnames(dataLoc)
colnames(dfRaw)
```
Now we combine our clean data into new dataset


```{r}
head(dataCategorized)
head(dataLoc)


```
```{r}
# We are selecting columns other than we have cleaned from Raw data into variable 'data1'and then merge into we cleaned.

data1 <- dfRaw |>select ('Do you understand that this is a paid course ?...3',
                "Course Fee Email",
                "Payment" ,
                "Payment Receipt Sent",
                "How and where did you hear about this course?",
                "Gender" ,
                "Age", 
                "Are you currently attending University / College?" , 
                "Have you taken any foundational course in data science / econometrics / statistics / computer science?",
                "What programming language(s) are you most comfortable in (R, Python, Java, JS, etc.)? If none please type \"None\".",
                "Prior Work Experience in Data Science or Machine Learning",
                "Primary Reason for taking this course?", 
                "Do you understand that this is a paid course ?...21", 
                "Prior Formal Education (course teaching or using R, university assignments, coding projects, course work, etc.) in R?",
                "Prior Formal Education (course teaching or using Python, university assignments, coding projects, course work, etc.) in Python?",
                "Prior Work Experience in R.",
                "Prior Work Experience in Python.",
                "Personal Education or Knowledge (learning R on your own and/or doing personal projects, etc.) in R?",
                "Do you have a LinkedIn Account?", 
                "Do you have any feedback, thoughts, or comments you would like to share?"
                )



```

```{r}
data2 <- cbind(dataCategorized, dataLoc)
colnames(data2)
datac <- data2 |> select( Id, Date, University, Degree, Country, City)

dataCleaned <- cbind(datac, data1)

```

```{r}
dim(dataCleaned)

write_csv(dataCleaned, "Data/dataCleaned1.csv")

```

