---
title: "Qasim DS Project 1"
author: "Qasim Basra"
date: "2022-09-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
<<<<<<< HEAD
=======
library(ggplot2)
>>>>>>> b114555 (Updated git ignore and Added Flexdashboard)
```

## Importing the Data

```{r , warning=FALSE,message=FALSE}

course_data <- read_csv("Data/Data - DS C1 Course.csv")


```

## Data Summary
```{r}
summary(course_data)

```

## Inspecting Columns names of the Data

```{r, echo=FALSE}

colnames(course_data)


<<<<<<< HEAD
```


=======

```

## Inspecting null values in the dataset

```{r}

is.na(course_data)

```

## Geometric Point Visulization of City student residing versus age

```{r}

ggplot(data= course_data,aes(x= Age, y=`Which City are you currently residing in?`))+
  geom_point()


```
>>>>>>> b114555 (Updated git ignore and Added Flexdashboard)













## Exploratory Data Analysis (EDA)


```{r EDA }


library(reticulate)

```

## Running Python in R
We will demonstrate how python will run in RStudio.

```{python}
import pandas as pd
import numpy as np
import seaborn as sns
import matplotlib.pyplot as plt
data= pd.read_csv("Data/Data - DS C1 Course.csv")
data_age= data["Age"].sort_values(ascending=False)
abc=list(data.columns)
data_age1=data[data["Age"]!= "Under 17"];
data_age1=data_age1.sort_values("Age");
sns.countplot("Age",data=data_age1)
plt.show()
```





